### 2021-06-25 Supplementary_Material/Regression_Trees_All.Rmd
regression trees update

#run  regression trees of the 3 metrics
set.seed(1)
tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0089891)

set.seed(1)
tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0159034)

set.seed(1)
tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0147899)

@@

#Set correct colnames for plotting
colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")

colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")

colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Mg of nectar", "Nectar concentration (%)","Pollen grains per flower")

set.seed(2)
tree1 <- rpart(Visits~., data=v_df, cp=0.0131325) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)

set.seed(2)
tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0109066) #6node divisons it is within on sd + error of best tree

set.seed(2)
tree3 <- rpart(Specialization~., data=d_df, cp=0.0147899) #7node divisons

>>>>

#run  regression trees of the 3 metrics
set.seed(1)
tree_1 <- rpart(Visits~., data=v_df_all, cp=0.0054559,minbucket=50)

set.seed(1)
tree_2 <- rpart(`Normalized degree`~., data=nd_df_all, cp=0.0084459,minbucket=50)

set.seed(1)
tree_3 <- rpart(Specialization~., data=d_df_all, cp=0.0072192 , minbucket=50) #10

@@

#Set correct colnames for plotting
colnames(v_df) <- c("Visits", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")

colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")

colnames(d_df) <- c("Specialization", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",   "Nectar concentration (%)","Pollen grains per flower")

set.seed(2)
tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)

set.seed(2)
tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)

set.seed(2)
tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50)

### 2021-06-25 Supplementary_Material/Regression_Trees_Subset_Nectar_Pollen.Rmd
regression trees update

colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")

@@

set.seed(2)
tree1 <- rpart(Visits~., data=v_df, cp=0.0154001)

set.seed(2)
tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0125459)

set.seed(2)
tree3 <- rpart(Specialization~., data=d_df, cp=0.0190352) 
par(mfrow=c(1,3))

rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1.25,type = 2) 
rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1.25,type = 2)
rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 1.15,type = 2)

>>>>

colnames(nd_df) <- c("Normalized degree", "Aut. selfing", "Flowers per plant", "Flower width", "Style length (mm)",
                      "Ovule number","Plant height (m)",  "Microlitres of nectar",  "Nectar concentration (%)","Pollen grains per flower")

@@

set.seed(2)
tree1 <- rpart(Visits~., data=v_df,  cp=0.009000,minbucket=50)

set.seed(2)
tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.005000,minbucket=50)

set.seed(2)
tree3 <- rpart(Specialization~., data=d_df, cp=0.0050000,minbucket=50) 
par(mfrow=c(1,3))

rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1.25,type = 2) 
rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1.25,type = 2)
rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 1.25,type = 2)
